Starspots on sub sub giants

### 2019-03-26 document/ms.tex
The observations sections have content filled in

\subsection{K2 superstamp lightcurves}
The \emph{Kepler} spacecraft targeted S0163 (EPIC 211414597) during the \emph{K2} mission \citep{howell14} in Campaigns 5, 16, 18 as part of the M67 superstamps.  The instrumental point spread function (PSF) of S1063 fell entirely within the oversized K2 target pixel files in Campaign 5 (K2 Custom Aperture ID 200008674) and Campaign 18 (K2 Custom Aperture ID 200233338).  Aperture photometry was conducted with interactively-assigned custom apertures using the \texttt{lightkurve .interact()} feature \citep{geert_barentsen_2019_2565212}. The apertures were chosen to minimize flux-loss out of the aperture due to spacecraft-induced image motion, while avoiding low-$S/N$ pixels and the wings of adjacent PSFs.  The Campaign 16 source PSF overlapped the border of two custom apertures (\textbf{numbers XX and XX}), which were stitched together before conducting aperture photometry.
We detrended motion-induced image artifacts with the Self Flat Field algorithm \citep{vanderburg14} implemented in \texttt{lightkurve}.  Postage stamp images are shown in Figure \textbf{ref XX}.

\begin{figure*}[htb!]
  \centering
  \begin{tabular}{ccccc}
    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_PS1_g.png}} &
    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_2M_J.png}} &
    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_K2_C5.png}} &
    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_K2_C16.png}} &
    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_K2_C18.png}} \\
  \end{tabular}
\caption{Imaging of S1063 in $60'' \times 60''$ postage stamps. \emph{left-to-right:} Pan-STARRS $g$-band co-added image contemporaneous with C16; 2MASS $J-$band; K2 Campaigns 5, 16, 18.}
\label{fig:imaging}
\end{figure*}

\subsection{Ground-based photometric monitoring}
The retrieved $V-$ band photometry from the All-Sky Automated Survey for Supernovae \citep[ASAS-SN][]{shappee14} using the ``Precomputed Light Curve'' provided in the Variable Stars Database (source ASASSN-V J085113.44+115139.7) and $g-$band photometry from the Sky Portal \citep{2017PASP..129j4502K}.  The $\sim8''$ pixels may cause some PSF blending of the nearby-albeit-fainter source seen at the bottom of Figure \ref{fig:imaging}.

\subsection{Gaia data}
M67 membership confirmed

@@

>>>>

\begin{figure*}[hbt!]
  \centering
  \begin{tabular}{ccccc}
    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_PS1_g.png}} &
    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_2M_J.png}} &
    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_K2_C5.png}} &
    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_K2_C16.png}} &
    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_K2_C18.png}} \\
  \end{tabular}
\caption{Imaging of S1063 in $60'' \times 60''$ postage stamps. \emph{left-to-right:} Pan-STARRS $g$-band co-added image contemporaneous with C16; 2MASS $J-$band; K2 Campaigns 5, 16, 18.}
\label{fig:imaging}
\end{figure*}

\subsection{K2 superstamp lightcurves}
The \emph{Kepler} spacecraft targeted S0163 (EPIC 211414597) during the \emph{K2} mission \citep{howell14} in Campaigns 5, 16, 18 as part of the M67 superstamps.  The instrumental point spread function (PSF) of S1063 fell entirely within the oversized K2 target pixel files in Campaign 5 (K2 Custom Aperture ID 200008674) and Campaign 18 (K2 Custom Aperture ID 200233338).  Aperture photometry was conducted with interactively-assigned custom apertures using the \texttt{lightkurve .interact()} feature \citep{geert_barentsen_2019_2565212}. The apertures were chosen to minimize flux-loss out of the aperture due to spacecraft-induced image motion, while avoiding low-$S/N$ pixels and the wings of adjacent PSFs.  The Campaign 16 source PSF overlapped the edge of Custom Aperture ID 200200534; a mosaic of adjacent superstamps was assembled before conducting aperture photometry.
We detrended motion-induced image artifacts with the Self Flat Field algorithm \citep{vanderburg14} implemented in \texttt{lightkurve}.  Postage stamp images are shown in Figure \ref{fig:imaging}.

\subsection{Ground-based photometric monitoring}
We retrieved All-Sky Automated Survey for Supernovae \citep[ASAS-SN][]{shappee14} lightcurves from the Sky Portal \citep{2017PASP..129j4502K}.  The lightcurves contained 758 epochs of $V-$ band photometry spanning 2013-2018 (source ASASSN-V J085113.44+115139.7) and 823 epochs of $g-$band photometry spanning mid-2017$-$2018.  The $\sim8''$ ASAS-SN pixels may cause some PSF blending of the nearby-albeit-fainter source seen at the bottom of Figure \ref{fig:imaging}.  The pixel images were not available to evaluate the extent of blending.
%% Option: Pan-STARRS

\subsection{Gaia data}
\emph{Gaia} DR2 astrometry \citep{2016A&A...595A...1G, 2018A&A...616A...1G} indicates a parallax ($1.17\pm0.025 \;$mas) and proper motion for S1063 (\emph{Gaia} DR2 604921030968952832) consistent with other M67 members, and approaching 100\% membership probability \citep{2018ApJ...869....9G}.

@@

%gaia
This work has made use of data from the European Space Agency (ESA) mission
{\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
has been provided by national institutions, in particular the institutions
participating in the {\it Gaia} Multilateral Agreement.
